Extended Data

### 2021-04-27 doc/manuscript/Dow_manuscript_Nature.Rmd
remove content on climwin results for Tmin
@camerondow35 , FYI, and let me know if you disagree. This is not central, and we don't have space for supporting figures/ tables (#52). We'll still show Tmin results for the April_May analysis and for the tree-rings.

For the majority of weekly time windows from Jan. 1 to $DOY_{25}$, there was a negative or neutral relationship between $T_{max}$ and $DOY_{25}$, meaning that warmer temperatures shifted growth earlier in the season (`r EDF_climwin`). 
This held true for both ring- and diffuse-porous trees at both sites, *albiet* with less consistent patterns at Harvard Forest, which was sampled for fewer years. 
The strongest relationships, including but not limited to the optimal time windows (`r  EDT_mean_growth_parameters`), occurred for time windows closing $\le$ 5 weeks prior to $DOY_{25}$.

The correlation of $DOY_{25}$ to $T_{min}$ was less consistent than that of $T_{max}$ (**NEEDS SUPPORTING FIG**). 
At SCBI, patterns were quite similar to those described above for $T_{max}$, with similar timing and strengths of correlations across the two temperature variables (**NEEDS SUPPORTING FIG**).
In contrast, at Harvard Forest, where we had only six years of data, *climwin* selected windows greater than five weeks prior to $DOY_{25}$, had positive correlations between $DOY_{25}$ and $T_{min}$.
However, for both ring- and diffuse- porous species, average $T_{min}$ of the selected period was below freezing (<0°C) in all years, suggesting that these are sporadic correlations that are unlikely to be biologically meaningful.

Henceforth, we focus on $T_{max}$ assessed over *climwin*-selected critical temperature windows, *noting that similar results are obtained using alternate temperature window ([GitHub issue #42](https://github.com/EcoClimLab/growth_phenology/issues/42)).*

>>>>

For the majority of weekly time windows from Jan. 1 to $DOY_{25}$, there was a negative or neutral relationship between $T_{max}$ and $DOY_{25}$, meaning that warmer temperatures shifted growth earlier in the season (`r EDF_climwin`). 
This held true for both ring- and diffuse-porous trees at both sites, *albiet* with less consistent patterns at Harvard Forest, which was sampled for fewer years. 
The strongest relationships, including but not limited to the optimal time windows (`r  EDT_mean_growth_parameters`), occurred for time windows closing $\le$ 5 weeks prior to $DOY_{25}$. 
Henceforth, we focus on $T_{max}$ assessed over *climwin*-selected critical temperature windows, *noting that similar results are obtained using alternate temperature window ([GitHub issue #42](https://github.com/EcoClimLab/growth_phenology/issues/42)).*
